A dynamic bioenergetic model for coral-\emph{Symbiodinium} symbioses and coral bleaching as an alternate stable state

### 2017-07-11 ms/ms.tex

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Alternate stable states in S:H biomass and growth across a
light gradient. Alternate stable states occur between
\textasciitilde{}25-42 mol photons m\textsuperscript{-2}
d\textsuperscript{-1} under these conditions (DIN=1e-7 mol N
L\textsuperscript{-1}; X=1e-7 C-mol X L\textsuperscript{-1}), depending
on whether initial S:H is high (1, closed circles), representing a
healthy coral, or low (0.0001, open circles), representing a bleached
coral. Arrow above point at L=25 indicates a S:H ratio beyond the axis
range; this `overshoot' phenomenon, in which initially bleached corals
may achieve high S:H ratios while remaining in a carbon-limited state is
discussed in the \emph{Coral Bleaching and Recovery} section.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig8.png}
\caption{Hysteresis under different nutrient and feeding regimes. Steady
state S:H biomass ratios in constant environments with (A) low DIN (1e-7
M) and low food (2e-7 M), (B) low DIN (1e-7 M) and no food, (C) high DIN
(2e-6 M) and low food (2e-7 M), and (D) high DIN (2e-6 M) and high food
(4e-7 M). In each panel, steady states are shown starting from both high
initial S:H biomass (1, i.e.~healthy corals - closed circles) and low
initial initial S:H biomass (0.0001, i.e.~bleached corals - open
circles). Points are colored according to whether the host exhibits
positive (black) or negative (red) growth at steady state.}
\end{figure}

>>>>

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig2.png}
\caption{Alternate stable states in S:H biomass and growth across a
light gradient. Alternate stable states occur between
\textasciitilde{}25-42 mol photons m\textsuperscript{-2}
d\textsuperscript{-1} under these conditions (DIN=1e-7 mol N
L\textsuperscript{-1}; X=1e-7 C-mol X L\textsuperscript{-1}), depending
on whether initial S:H is high (1, closed circles), representing a
healthy coral, or low (0.0001, open circles), representing a bleached
coral. Arrow above point at L=25 indicates a S:H ratio beyond the y-axis
range; this `overshoot' phenomenon, in which initially bleached corals
may achieve high S:H ratios while remaining in a carbon-limited state is
discussed in the \emph{Coral Bleaching and Recovery} section.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics{../img/Fig8.png}
\caption{Hysteresis under different nutrient and feeding regimes. Steady
state S:H biomass ratios in constant environments with (A) low DIN (1e-7
M) and low food (2e-7 M), (B) low DIN (1e-7 M) and no food, (C) high DIN
(2e-6 M) and low food (2e-7 M), and (D) high DIN (2e-6 M) and high food
(4e-7 M). In each panel, steady states are shown starting from both high
initial S:H biomass (1, i.e.~healthy corals - closed circles) and low
initial initial S:H biomass (0.0001, i.e.~bleached corals - open
circles). Points are colored according to whether the host exhibits
positive (black) or negative (red) growth at steady state. Arrows above
points indicate values beyond the y-axis range.}
\end{figure}
